---
title: "FIA Center Boundaries Analysis"
output:
  html_notebook: default
  html_document: default
  pdf_document: default
---

```{r Setup, message=FALSE, warning=FALSE, include=FALSE}
library(BCDSS)
LoadPackages(c('tidyverse', 'rio','ggmap', 'lubridate', 'scales', 'stringr', 'knitr', 'tidyr', 'ggrepel'))
gis <- "S:/Innovation Office/Misc/GIS/Shape Files"

# Getting cleaned data ####
df <- GetCARES()
#save(cases, file="cases.RData")

# Final cleaned data

cases <- list(
     hoh = df %>% filter(`HOH IRN` == `CARES ID`) %>%
          group_by(`HOH IRN`) %>%
          mutate(`Program Count` = n_distinct(`Program Code`)) %>%
          distinct(`HOH IRN`, .keep_all = TRUE) %>%
          ungroup(),
     au = df %>%
          group_by(`HOH IRN`) %>%
          mutate(`Program Count` = n_distinct(`Program Code`)) %>%
          ungroup() %>% 
          distinct(`AU #`, .keep_all = TRUE),
     client = df %>%
          group_by(`HOH IRN`) %>%
          mutate(`Program Count` = n_distinct(`Program Code`)) %>%
          ungroup() %>% 
          distinct(`CARES ID`, .keep_all = TRUE)) %>%
     lapply(filter, `AU Status Code` == "A" & `Ldss Id` == 30) %>%
     lapply(select, `District Office #`, First, Last, `CARES ID`, `AU #`, `Program Code`, `Program Count`,
          `Fin Responsibility`, `HOH IRN`, `Redetermination End Date`, Birthdate,
          `Residential Zip Code`, `MA Coverage Group`, `Application ID`)

works <- read.csv('S:/Innovation Office/familyinvestment/all/caseequal/swredist/fia_all_casequal_swredist_dat_works_170817.csv', header=TRUE, stringsAsFactors=FALSE)
names(works) <- RenameCol(works)
works <- select(works, `Client ID`, `Participation Status Code`,`Activity Subcode`,
     `Exemption Reason`)
```


```{r Parameters, warning = FALSE, include=FALSE}
params <- list(
     new = list(
          `Dunbar-Orangeville` = c(21205, 21222, 21224, 21231, 21237, 21287),
          `Harbor View` = c(21225, 21227, 21230, 21226),
          `Hilton Heights` = c(21223, 21228, 21229),
          `Penn-North` = c(21201, 21216, 21217),
          Northwest = c(21207, 21208, 21209, 21210, 21211, 21215),
          `Northeast Regional Office` = c(21202, 21206, 21212, 21213, 21214, 21218, 21234, 21236, 21239, 21251)),
     current = list(
          `Dunbar-Orangeville` = c(21205, 21222, 21224, 21231, 21237, 21287),
          `Harbor View` = c(21225, 21227, 21230, 21226),
          `Hilton Heights` = c(21216, 21223, 21228, 21229),
          `Penn-North` = c(21201, 21217),
          Northwest = c(21207, 21208, 21209, 21210, 21211, 21215),
          `Northeast Regional Office` = c(21202, 21206, 21212, 21213, 21214, 21218, 21234, 21236, 21239, 21251)))

print(params$new)
```

```{r Reference dfs, warning = FALSE, include=FALSE}

centers.base <- data.frame(Zip = c(21201, 21202, 21205, 21206, 21207, 21208,
          21209, 21210, 21211, 21212, 21213, 21214, 21215, 21216, 21217, 21218, 
          21222, 21223, 21224, 21225, 21226, 21227, 21228, 21229, 21230, 21231, 
          21234, 21236, 21237, 21239, 21251, 21287), Center = NA) %>%
     mutate(Zip = as.character(Zip))

codes <- data.frame(Center = c("Harbor View", "Hilton Heights", "Northwest",
                    "Penn-North", "Dunbar-Orangeville", "Northeast Regional Office",
                    "Southwest", "Training Region", "E-Applications", "Central MA",
                    "Central Foster Care MA", "Resettlement Center", "Health Department"),
                    Code = c(332, 344, 340, 346, 341, 337, 345, 300, 336, 353, 356, 370, 399)) %>%
     mutate(Center = as.character(Center))

# Outpost workers taken from BCDSS roster Google Sheet on 7/18/2017
codes$Outpost[codes$Center == "Dunbar-Orangeville"] <- 8
codes$Outpost[codes$Center == "Harbor View"] <- 0
codes$Outpost[codes$Center == "Penn-North"] <- 8
codes$Outpost[codes$Center == "Northwest"] <- 1
codes$Outpost[codes$Center == "Northeast Regional Office"] <- 2
codes$Outpost[codes$Center == "Hilton Heights"] <- 2

centers <- centers.base
      

for (i in names(params[["new"]])){
          centers$Center[centers$Zip %in% params[["new"]][[i]]] <- i}

     centers <- left_join(centers, codes)
```

# Context
In July 2017, FIA is transitioning its centers' boundaries to align with zip code boundaries. 

```{r Maps, echo=FALSE, message=FALSE, warning=FALSE}

maps <- list(current = NA,
             new = NA,
             base = ggmap(get_map(geocode("Baltimore, MD"),
                    zoom = 12, scale = 1, maptype = "toner-lite", source="stamen"),
                    extent="device", maprange = FALSE))

map.sites <- GetMapElements("site") %>%
     filter(Type == "Family Investment") %>%
     mutate(`Site Name` = str_wrap(`Site Name`, 10))
map.zips <- GetMapElements("zipcode")

map.bounds <- left_join(map.zips, centers, by = c("zip" = "Zip"))

# Create map
for (i in c("new", "current")){
     maps[[i]] <- maps[["base"]] +
          geom_polygon(data = map.bounds, aes(x = long, y = lat, group = group, fill = Center),
               size = .5, alpha = .7) +
          geom_text(data = map.bounds,  size = 4, fontface = 'bold',
               aes(label = zip, x = centroid.long, y = centroid.lat)) +
          geom_point(data = map.sites, aes(x = long, y = lat), size = 4,
               shape = 17, color = "white") +
          geom_text(data = map.sites, color = "white", size = 5, fontface = 'bold',
               aes(label = `Site Name`, x = long, y = lat - .006)) + 
          labs(#title = paste(str_to_title(i), "Boundaries"),
                   fill = "Zip Codes Assigned to Center")
}
```


## New boundaries
Center boundaries were realigned with zip codes in order to balance caseloads and simplify case assignment:


```{r Zipcode assignments, echo=FALSE, message=FALSE, warning=FALSE}
kable(centers$new %>%
     filter(Active == "Yes") %>%
     select(Zip, Center) %>%
     arrange(Center, Zip))
```

```{r New map, echo=FALSE, message=FALSE, warning=FALSE, fig.height=6, fig.width=6}
print(maps$new)
```

We will be transitioning cases to their respective centers according to these new boundaries a center at a time, according to this schedule:

```{r Schedule, echo=FALSE, message=FALSE, warning=FALSE}
centers$new %>%
     select(Center, schedule) %>%
     distinct(Center, .keep_all = TRUE) %>%
     filter(!is.na(schedule)) %>%
     arrange(schedule) %>%
     kable()
```


```{r Matching centers to households, warning = FALSE, include=FALSE}
zips <- centers$Zip

caseload <- cases %>%
     lapply(left_join, centers, by = c("Residential Zip Code" = "Zip")) %>%
     lapply(left_join,distinct(centers[c("Center", "Code")]), 
            by = c("District Office #" = "Code")) %>%
     lapply(rename, `Current FIA Center Code` = `District Office #`, 
            `New FIA Center` = `Center.x`, `New FIA Center Code` = Code,
            `Current FIA Center` = `Center.y`) %>%
     # 353 PAA stays, other program types at 353 go to respective centers   
     lapply(mutate, `New FIA Center` = ifelse(`Current FIA Center Code` == 353 &
                                                   `Program Code` == "PA", "Central MA", `New FIA Center`),
            `New FIA Center Code` = ifelse(`Current FIA Center Code` == 353 &
                                                `Program Code` == "PA", 353, `New FIA Center Code`),
            `Current FIA Center` = ifelse(`Current FIA Center Code` == 353,
                                          "Central MA", `Current FIA Center`)) %>%
     # 356 stays at foster care MA
     lapply(mutate, `New FIA Center` = ifelse(`Current FIA Center Code` == 356,
                                              "Central Foster Care MA", `New FIA Center`),
            `New FIA Center Code` = ifelse(`Current FIA Center Code` == 356,
                                           356, `New FIA Center Code`),
            `Current FIA Center` = ifelse(`Current FIA Center Code` == 356,
                                          "Central Foster Care MA", `Current FIA Center`)) %>%
     # 399 stays at city health dept
     lapply(mutate, `New FIA Center` = ifelse(`Current FIA Center Code` == 399,
                                              "Health Department", `New FIA Center`),
            `New FIA Center Code` = ifelse(`Current FIA Center Code` == 399,
                                           399, `New FIA Center Code`),
            `Current FIA Center` = ifelse(`Current FIA Center Code` == 399,
                                          "Health Department", `Current FIA Center`)) %>%
     # 370 stays at resettlement center and after a few months they can go anywhere in the state
     lapply(mutate, `New FIA Center` = ifelse(`Current FIA Center Code` == 370,
                                              "Resettlement Center", `New FIA Center`),
            `New FIA Center Code` = ifelse(`Current FIA Center Code` == 370,
                                           370, `New FIA Center Code`),
            `Current FIA Center` = ifelse(`Current FIA Center Code` == 370,
                                          "Resettlement Center", `Current FIA Center`)) %>%
     # HOHs with only MA S02 cases to 353 Central MA
     lapply(mutate, `New FIA Center` = ifelse((`Program Count` == 1 &
                    !is.na(`MA Coverage Group`) & `MA Coverage Group` == "S02"),
                    "Central MA", `New FIA Center`),
            `New FIA Center Code` = ifelse((`Program Count` == 1 & 
                    !is.na(`MA Coverage Group`) & `MA Coverage Group` == "S02"),
                    353, `New FIA Center Code`)) %>%
     # Out of county
     lapply(mutate, `New FIA Center` = ifelse(!`Residential Zip Code` %in% zips,
                                              "Out of County", `New FIA Center`),
            `New FIA Center Code` = ifelse(!`Residential Zip Code` %in% zips,
                                           0, `New FIA Center Code`)) %>%
     # Really old DOs
     lapply(mutate, `Current FIA Center` = ifelse(is.na(`Current FIA Center`), "Old DO",
                                                  `Current FIA Center`))

rm(zips)
```

```{r Transfers: Penn-North}

penn.in <- caseload %>%
     lapply(filter, `New FIA Center` == "Penn-North") %>%
     lapply(count, `Current FIA Center`)


penn.out <- caseload %>%
     lapply(filter, `Current FIA Center` == "Penn-North") %>%
     lapply(count, `New FIA Center`)


# Penn Jan Redets
test <- new.redets.master %>% filter(`New FIA Center` == "Penn-North" | `Current FIA Center` == "Penn-North", !(`New FIA Center` == "Penn-North" & `Current FIA Center` == "Penn-North"), month(`Redetermination End Date`) == 1, year(`Redetermination End Date`) == 2018) %>%           select(`HOH IRN`, Last, First, `Current FIA Center`,
                 `Redetermination End Date`, `New Redetermination Date`, `New FIA Center`)

# Dividing by 08 level staff
penn.transfers <- caseload[["hoh"]] %>%
     filter((`New FIA Center` == "Penn-North" | `Current FIA Center` == "Penn-North") &
                 !(`New FIA Center` == "Penn-North" & `Current FIA Center` == "Penn-North")) %>%
     select(`HOH IRN`, `First`, `Last`, Birthdate, `Residential Zip Code`,
            `Current FIA Center`, `Current FIA Center Code`, `New FIA Center`, `New FIA Center Code`)

level08 <- import("CARES Access Level 08.xlsx", which = "Summary") %>%
     # each staff can transfer 3/hr and can work 2 hr/day
     mutate(`Case transfers per day` = `08 Level Staff` * 3 * 2,
            `Total cases to process` = round(`Case transfers per day` *
                 (nrow(penn.transfers) / sum(`Case transfers per day`))),
            CumSum = cumsum(`Total cases to process`)) # days to complete transfers) 

ExportExcel(level08, "Schedule Summary", "Penn North Case Transfer Assignments.xlsx", "new")



level08.units <- list()

start <- 1

for (i in level08$DO) {
     end <- level08$CumSum[level08$DO == i]
     level08.units[[i]] <- penn.transfers[start:end,]
     start <- end + 1
     ExportExcel(level08.units[[i]], i, "Penn North Case Transfer Assignments.xlsx", "existing")
}



```


```{r Caseload equalization, include=FALSE}
equal <- list(
     cases = caseload$au %>% 
          mutate(`CARES ID` = as.numeric(`CARES ID`))%>% 
          left_join(works, by = c("CARES ID" = "Client ID")) %>% ## Criterion 1: Active cases (already done)
          filter(!duplicated(`AU #`), ## Criterion 2: Deduplicated AU numbers
          !(`MA Coverage Group` %in% c("S02","T01","T02","T03","T04","T05", "T99", "L01",
               "L98","L99"))), ## Criterion 3: MA coverage codes as proxies for SSI, exclude codes  

# MD HEALTH CONNECTION ####
## MA numbers include those customers who have cases in MHC. Even though MHC
## customers are responsible for renewing their MA coverage on their own, it
## still affects the center's workload. MHC customers often use the SAIL labs to 
## complete renewals and staff provide reminders/assistance.

# What we are doing in this section is creating a 'new' record for each HX case
# because CARES does not capture each case separately like all the other
# benefits

## Finding only active cases with HX codes
     mhc = caseload$au %>% 
          mutate(`CARES ID` = as.numeric(`CARES ID`)) %>% 
          left_join(works, by = c("CARES ID" = "Client ID")) %>%
          filter(`Application ID` == "HX") %>%

## Exclude ALL CASES for people who have both an MA program code + HX app ID
## because we already counted them as an MA case when we filter for the
## overall criteria

## Clients who have HX codes have those codes across all their benefit types;
## we will be counting MHC cases by a (deduplicated) record of any type of 
## benefit associated with an HX code. This is a proxy for having a record for
## benefit type HX. For this reason, we want to make sure we exclude all 
## records, regardless of benefit, for people who have an MA + HX code.

## Filtering out all records associated with an MA+HX combo
          mutate(ma.hx = ifelse(`Program Code` == "MA" & `Fin Responsibility` == "RE", 1, 0)) %>%
          group_by(`CARES ID`) %>%
          filter(sum(ma.hx) < 1) %>%
## Deduplicate HOH IRNs because the HX code 
          distinct(`HOH IRN`, .keep_all = TRUE) %>%
          mutate(`Program Code` = "HX") %>%
          select(-ma.hx))

equal <- merge(equal$cases, equal$mhc, all = TRUE)

caseload.equal <- equal %>%
     count(`New FIA Center`) %>%
     rename(Center = `New FIA Center`, `Equalized Caseload after Reassignment` = n) %>%
     left_join(equal %<>%
                    count(`Current FIA Center`) %>%
                    rename(Center = `Current FIA Center`, `Equalized Caseload Currently` = n))

```


```{r Planning numbers, warning = FALSE, echo=FALSE}
planning <- rep(list(list(transfers = NA, transfers.graph = NA, redets = NA, redets.graph = NA)), 6)
names(planning) <- names(params$new)

for (i in names(params$new)){
# Transfers
     planning[[i]]$transfers <- caseload$hoh %>%
          filter(`New FIA Center` == i, `Current FIA Center` != i)
     planning[[i]]$transfers <- as.data.frame(
          table(planning[[i]]$transfers$`Current FIA Center`)) %>%
          mutate(Var1 = as.character(Var1)) %>%
          arrange(desc(Freq))
# Transfers Graph
     planning[[i]]$transfers.graph <- planning[[i]]$transfers %>%
          ggplot(aes(Var1, Freq)) +
               geom_histogram(stat="identity", fill = "skyblue4") + theme_minimal() +
               geom_text(aes(label = Freq),
                    position = position_dodge(width = 1), 
                    vjust = -.1, size = 3, fontface = "bold") +
               theme(plot.title = element_text(size = 15, face = "bold"),
                     axis.title.x = element_blank(), 
                     axis.text.x = element_text(angle = 90, hjust = 1),
                     legend.position = "none") +
               scale_y_continuous(breaks = pretty_breaks(n = 10)) +
               labs(title = "Centers from which Cases are Transferring",
                    y = "Cases")
# Redet Dates
     planning[[i]]$redets <- caseload$hoh %>% filter(`New FIA Center` == i) %>%
          mutate(`Redetermination End Date` = month(`Redetermination End Date`,
               label = TRUE, abbr = TRUE))
     planning[[i]]$redets <- as.data.frame(
          table(planning[[i]]$redets$`Redetermination End Date`))
     names(planning[[i]]$redets) <- c("Month of Redet", "Current Number of Cases")
     planning[[i]]$redets$`Cases to Move` <-
          round(mean(planning[[i]]$redets$`Current Number of Cases`)) - 
               planning[[i]]$redets$`Current Number of Cases`
     
     
# Redet Dates Graph
     planning[[i]]$redets.graph <- planning[[i]]$redets %>%
          ggplot(aes(`Month of Redet`, `Current Number of Cases`)) +
               geom_histogram(stat="identity", fill = "skyblue4") + theme_minimal() +
               geom_text(aes(label = `Current Number of Cases`),
                    position = position_dodge(width = 1),
                    vjust = -.1, size = 3, fontface = "bold") +
               theme(plot.title = element_text(size = 15, face = "bold"),
                     axis.title.x = element_blank(),
                     legend.position = "none") +
               scale_y_continuous(breaks = pretty_breaks(n = 10)) +
               labs(title = "Months with Scheduled Redeterminations",
                    y = "Cases")
     }

```

```{r Reassign cases, include=FALSE, warning=FALSE}

new.redets <- rep(list(list(cases = NA, summary = NA)), 6)
names(new.redets) <- names(params$new)

for (i in names(params$new)) {
     # Create summary frame that shows how many cases still need to be moved
     # from month to month
     new.redets[[i]]$summary <- planning[[i]]$redets %>%
          arrange(`Cases to Move`) %>%
          mutate(`Month of Redet` = as.character(`Month of Redet`))
     
     # Create frame where each case will be given a new redet date
     new.redets[[i]]$cases <- caseload$hoh %>%
          filter(`New FIA Center` == i) %>%
          mutate(`New Redetermination Date` = NA)
     
     # Continue reassigning while there are still cases to be moved
     while (max(abs(new.redets[[i]]$summary$`Cases to Move`)) > 3) {
          highest.month <- new.redets[[i]]$summary$`Month of Redet`[[1]]
          highest.space <- new.redets[[i]]$summary$`Cases to Move`[[1]]
          lowest.month <- new.redets[[i]]$summary$`Month of Redet`[[12]]
          lowest.space <- new.redets[[i]]$summary$`Cases to Move`[[12]]
          
          
          # Identify which cases currently assigned to month with most cases
          new.redets[[i]]$cases %<>%
               mutate(`Highest Month` = as.character(month(`Redetermination End Date`,
                    label = TRUE, abbr = TRUE)) == highest.month) %>%
               arrange(desc(`Highest Month`), !is.na(`New Redetermination Date`)) %>%
               select(-`Highest Month`)
          
          # Only move as many cases as there is space
          if (abs(highest.space) >= lowest.space) { 
               new.redets[[i]]$cases$`New Redetermination Date`[1:lowest.space] <-
                    lowest.month
          } else if (abs(highest.space) < lowest.space) { 
               new.redets[[i]]$cases$`New Redetermination Date`[1:abs(highest.space)] <-
                    lowest.month
          } else {
               break
               }
          
# Redet Dates
     new.redets[[i]]$summary <- new.redets[[i]]$cases %>%
          mutate(`Final Redetermination Date` = ifelse(is.na(`New Redetermination Date`),
               as.character(month(`Redetermination End Date`, label = TRUE, abbr = TRUE)),
               `New Redetermination Date`))
     new.redets[[i]]$summary <- as.data.frame(
          table(new.redets[[i]]$summary$`Final Redetermination Date`))
     new.redets[[i]]$summary <- new.redets[[i]]$summary %>%
          rename("Month of Redet" = Var1, "Current Number of Cases" = Freq) %>%
          mutate(`Cases to Move` = round(mean(`Current Number of Cases`)) - 
               `Current Number of Cases`,
               `Month of Redet` = as.character(`Month of Redet`)) %>%
          arrange(`Cases to Move`)
     
     cat(i, max(abs(new.redets[[i]]$summary$`Cases to Move`), "| "))
     }
     
     if(exists("new.redets.master")){
          new.redets.master <- rbind(new.redets.master, new.redets[[i]]$cases)
     }
     else{ new.redets.master <- new.redets[[i]]$cases
     }
}

# Generate list of redets for upcoming month, by current FIA center
# This is used at each center to change 
transfers <- new.redets.master %>%
     select(`HOH IRN`, Last, First, `Current FIA Center`,
            `Redetermination End Date`, `New Redetermination Date`, `New FIA Center`) %>%
     arrange(`Redetermination End Date`) %>%
     filter(!is.na(`New Redetermination Date`) | `Current FIA Center` != `New FIA Center`)

for (i in names(params$new)){
     master <- new.redets.master %>%
          select(`HOH IRN`, Last, First, `Current FIA Center`,
                 `Redetermination End Date`, `New Redetermination Date`, `New FIA Center`) %>%
          arrange(`Redetermination End Date`) %>%
          filter(`Current FIA Center` == i,
                 !is.na(`New Redetermination Date`) | `Current FIA Center` != `New FIA Center`)
     
     transfers <- master %>% filter(`Current FIA Center` != `New FIA Center`)
          
     redets <- master %>% filter(`Current FIA Center` == `New FIA Center`) %>% select(-`New FIA Center`)
     
     summary <- as.data.frame(Transfers = nrows(transfers), Redets = nrows(redets))
     
     ExportExcel(transfers, "Transfers", paste0("Outputs/", i, " Transactions.xlsx"), "new")
     ExportExcel(redets, "Redets", paste0("Outputs/", i, " Transactions.xlsx"), "existing")
     
}

```


```{r Summary, warning = FALSE, include=FALSE}
# Staffing
staff <- GetFullStaff("Family Investment")

clerks <- staff %>% 
     filter(`Job Title` %in% c("Administrative Specialist Trainee", "Fiscal Accounts Clerk ",
               "Fiscal Accounts Clerk II","Fiscal Clerk II","Office Assistant", "Office Clerk",
               "Office Clerk Assistant","Office Clerk I","Office Clerk II",
               "Office Processing Clerk II","Office Services Clerk","Office Services Clerk II"),
          Program %in% c("Northeast Regional Office", "Penn-North",
               "Dunbar-Orangeville", "Harbor View", "Northwest", "Hilton Heights"),
          `Manager ID` != "W1058936") %>% # Removes specialized CCU unit
     select(`Employee ID`, `Job Title`, `Program`) %>%
     count(Program) %>%
     rename(`Center` = Program, `Clerks Currently at Center` = n)

fis <- staff %>% 
     filter(`Job Title` %in% c("Family Investment Spec I", "Family Investment Spec II"),
          Program %in% c("Northeast Regional Office", "Penn-North",
               "Dunbar-Orangeville", "Harbor View", "Northwest", "Hilton Heights"),
          `Manager ID` != "W1058936") %>% # Removes specialized CCU unit
     select(`Employee ID`, `Job Title`, `Program`) %>%
     count(Program) %>%
     rename(`Center` = Program, `FIS Is/IIs Currently at Center` = n) %>%
     left_join(clerks) %>%
     left_join(codes)

# Cross-tab
summary <- list(
     hoh = caseload$hoh %>%
          count(`Current FIA Center`) %>%
          rename(Center = `Current FIA Center`, `Households Currently at Center` = n) %>%
          full_join(caseload$hoh %>%
                         count(`New FIA Center`) %>%
                         rename(Center = `New FIA Center`, `Households at Center after Reassignment` = n)) %>%
          left_join(fis) %>%
          mutate(`FIS Is/IIs Currently at Center` = as.integer(`FIS Is/IIs Currently at Center` - Outpost),
                 `Household Difference` = `Households at Center after Reassignment` -
                      `Households Currently at Center`) %>%
          select(-Outpost, -Code),
     client = caseload$client %>%
          count(`Current FIA Center`) %>%
          rename(Center = `Current FIA Center`, `Clients Currently at Center` = n) %>%
          full_join(caseload$client %>%
                         count(`New FIA Center`) %>%
                         rename(Center = `New FIA Center`, `Clients at Center after Reassignment` = n)) %>%
          mutate(`Client Difference` = `Clients at Center after Reassignment` -
                      `Clients Currently at Center`))

summary$master <- left_join(summary$hoh, summary$client) %>%
     left_join(caseload.equal)

summary$main <- summary$master %>%
     filter(Center %in% centers$Center) %>%
     select(-`FIS Is/IIs Currently at Center`, -`Clerks Currently at Center`,
            -`Equalized Caseload Currently`, -`Equalized Caseload after Reassignment`)
summary$other <- summary$master %>%
     filter(!Center %in% centers$Center) %>%
     select(-`FIS Is/IIs Currently at Center`, -`Clerks Currently at Center`,
            -`Equalized Caseload Currently`, -`Equalized Caseload after Reassignment`)
summary$fis <- summary$master %>%
     filter(Center %in% centers$Center) %>%
     select(Center, `Equalized Caseload Currently`, `Equalized Caseload after Reassignment`,
            `FIS Is/IIs Currently at Center`) %>%
     mutate(`FIS Is/IIs Caseload Ratio Currently` = as.integer(`Equalized Caseload Currently`
                                                               / `FIS Is/IIs Currently at Center`),
            `FIS Is/IIs Caseload Ratio after Reassignment` = as.integer(`Equalized Caseload after Reassignment`
                                                                        / `FIS Is/IIs Currently at Center`),
            `FIS Is/IIs to Move after Reassignment for 1:915 Caseload` =
                 round(`Equalized Caseload after Reassignment`/915) - `FIS Is/IIs Currently at Center`)
summary$clerk <- summary$master %>%
     filter(Center %in% centers$Center) %>%
     select(Center, `Equalized Caseload Currently`, `Equalized Caseload after Reassignment`,
            `Clerks Currently at Center`) %>%
     mutate(`Clerk Caseload Ratio Currently` = as.integer(`Equalized Caseload Currently`
                                                          / `Clerks Currently at Center`),
            `Clerk Caseload Ratio after Reassignment` = as.integer(`Equalized Caseload after Reassignment`
                                                                   / `Clerks Currently at Center`),
            `Clerk to Move after Reassignment for 1:2700 Caseload` =
                 round(`Equalized Caseload after Reassignment`/2700) - `Clerks Currently at Center`)
```

```{r Final, warning = FALSE, include=FALSE}
final <- rep(list(list(month.highest = NA, month.lowest = NA, 
     transfer1 = NA, transfer2 = NA, staff.move = NA)), 6)
names(final) <- names(params$new)

for (i in names(params$new)) {
final[[i]]$month.highest <- as.character(
     planning[[i]]$redets$`Month of Redet`[planning[[i]]$redets$`Current Number of Cases` ==
          max(planning[[i]]$redets$`Current Number of Cases`)])
final[[i]]$month.lowest <- as.character(
     planning[[i]]$redets$`Month of Redet`[planning[[i]]$redets$`Current Number of Cases` ==
          min(planning[[i]]$redets$`Current Number of Cases`)])
final[[i]]$transfer1 <- planning[[i]]$transfers$Var1[[1]]
final[[i]]$transfer2 <-  planning[[i]]$transfers$Var1[[2]]
final[[i]]$staff.move <- summary$`Staff to Move to New Center for 1:900 Caseload`[summary$Center == i]
final[[i]]$month.avg <- as.character(round(mean(planning[[i]]$redets$`Current Number of Cases`)))
}
```



# Dunbar-Orangeville
### Cases to transfer between centers
When cases are realigned, most of the cases coming to Dunbar-Orangeville will be coming from `r final[["Dunbar-Orangeville"]]$transfer1` and `r final[["Dunbar-Orangeville"]]$transfer2`.

```{r Dunbar-Orangeville transfers, echo=FALSE, message=FALSE, warning=FALSE}
print(planning[["Dunbar-Orangeville"]]$transfers.graph)
```

### Current spread of redeterminations
When cases are realigned, the month of `r final[["Dunbar-Orangeville"]]$month.highest` will have the most redeterminations while the month of `r final[["Dunbar-Orangeville"]]$month.lowest` will have the fewest.

```{r Dunbar-Orangeville redets, echo=FALSE, message=FALSE, warning=FALSE}
print(planning[["Dunbar-Orangeville"]]$redets.graph)
```

In order to ensure that redeterminations are done evenly throughout the year, there should be about `r final[["Dunbar-Orangeville"]]$month.avg` cases processed each month. To achieve that, cases should be moved as such:
`r kable(planning[["Dunbar-Orangeville"]]$redets)`


### Staff to transfer between centers
An estimated `r abs(final[["Dunbar-Orangeville"]]$staff.move)` FIS Is/IIs need to be moved `r ifelse(final[["Dunbar-Orangeville"]]$staff.move > 0, print("to"), print("from"))` Dunbar-Orangeville to balance caseloads across all centers:

```{r Dunbar-Orangeville staffing, echo=FALSE, message=FALSE, warning=FALSE}
summary %>% filter(Center == "Dunbar-Orangeville")  %>% select(-`Center Code`, -Center) %>% kable()
```



# Harbor View
### Cases to transfer between centers
When cases are realigned, most of the cases coming to Harbor View will be coming from `r final[["Harbor View"]]$transfer1` and `r final[["Harbor View"]]$transfer2`.

```{r Harbor View transfers, echo=FALSE, message=FALSE, warning=FALSE}
print(planning[["Harbor View"]]$transfers.graph)
```

### Current spread of redeterminations
When cases are realigned, the month of `r final[["Harbor View"]]$month.highest` will have the most redeterminations while the month of `r final[["Harbor View"]]$month.lowest` will have the fewest.

```{r Harbor View redets, echo=FALSE, message=FALSE, warning=FALSE}
print(planning[["Harbor View"]]$redets.graph)
```

In order to ensure that redeterminations are done evenly throughout the year, there should be about `r final[["Harbor View"]]$month.avg` cases processed each month. To achieve that, cases should be moved as such:
`r kable(planning[["Harbor View"]]$redets)`


### Staff to transfer between centers
An estimated `r abs(final[["Harbor View"]]$staff.move)` FIS Is/IIs need to be moved `r ifelse(final[["Harbor View"]]$staff.move > 0, print("to"), print("from"))` Harbor View to balance caseloads across all centers:

```{r Harbor View staffing, echo=FALSE, message=FALSE, warning=FALSE}
summary %>% filter(Center == "Harbor View")  %>% select(-`Center Code`, -Center) %>% kable()
```



# Penn-North
### Cases to transfer between centers
When cases are realigned, most of the cases coming to Penn-North will be coming from `r final[["Penn-North"]]$transfer1` and `r final[["Penn-North"]]$transfer2`.

```{r Penn-North transfers, echo=FALSE, message=FALSE, warning=FALSE}
print(planning[["Penn-North"]]$transfers.graph)
```

### Current spread of redeterminations
When cases are realigned, the month of `r final[["Penn-North"]]$month.highest` will have the most redeterminations while the month of `r final[["Penn-North"]]$month.lowest` will have the fewest.

```{r Penn-North redets, echo=FALSE, message=FALSE, warning=FALSE}
print(planning[["Penn-North"]]$redets.graph)
```

In order to ensure that redeterminations are done evenly throughout the year, there should be about `r final[["Penn-North"]]$month.avg` cases processed each month. To achieve that, cases should be moved as such:
`r kable(planning[["Penn-North"]]$redets)`


### Staff to transfer between centers
An estimated `r abs(final[["Penn-North"]]$staff.move)` FIS Is/IIs need to be moved `r ifelse(final[["Penn-North"]]$staff.move > 0, print("to"), print("from"))` Penn-North to balance caseloads across all centers:

```{r Penn-North staffing, echo=FALSE, message=FALSE, warning=FALSE}
summary %>% filter(Center == "Penn-North")  %>% select(-`Center Code`, -Center) %>% kable()
```



# Northwest
### Cases to transfer between centers
When cases are realigned, most of the cases coming to Northwest will be coming from `r final[["Northwest"]]$transfer1` and `r final[["Northwest"]]$transfer2`.

```{r Northwest transfers, echo=FALSE, message=FALSE, warning=FALSE}
print(planning[["Northwest"]]$transfers.graph)
```

### Current spread of redeterminations
When cases are realigned, the month of `r final[["Northwest"]]$month.highest` will have the most redeterminations while the month of `r final[["Northwest"]]$month.lowest` will have the fewest.

```{r Northwest redets, echo=FALSE, message=FALSE, warning=FALSE}
print(planning[["Northwest"]]$redets.graph)
```

In order to ensure that redeterminations are done evenly throughout the year, there should be about `r final[["Northwest"]]$month.avg` cases processed each month. To achieve that, cases should be moved as such:
`r kable(planning[["Northwest"]]$redets)`


### Staff to transfer between centers
An estimated `r abs(final[["Northwest"]]$staff.move)` FIS Is/IIs need to be moved `r ifelse(final[["Northwest"]]$staff.move > 0, print("to"), print("from"))` Northwest to balance caseloads across all centers:

```{r Northwest staffing, echo=FALSE, message=FALSE, warning=FALSE}
summary %>% filter(Center == "Northwest")  %>% select(-`Center Code`, -Center) %>% kable()
```



# Northeast Regional Office
### Cases to transfer between centers
When cases are realigned, most of the cases coming to Northeast Regional Office will be coming from `r final[["Northeast Regional Office"]]$transfer1` and `r final[["Northeast Regional Office"]]$transfer2`.

```{r Northeast Regional Office transfers, echo=FALSE, message=FALSE, warning=FALSE}
print(planning[["Northeast Regional Office"]]$transfers.graph)
```

### Current spread of redeterminations
When cases are realigned, the month of `r final[["Northeast Regional Office"]]$month.highest` will have the most redeterminations while the month of `r final[["Northeast Regional Office"]]$month.lowest` will have the fewest.

```{r Northeast Regional Office redets, echo=FALSE, message=FALSE, warning=FALSE}
print(planning[["Northeast Regional Office"]]$redets.graph)
```

In order to ensure that redeterminations are done evenly throughout the year, there should be about `r final[["Northeast Regional Office"]]$month.avg` cases processed each month. To achieve that, cases should be moved as such:
`r kable(planning[["Northeast Regional Office"]]$redets)`


### Staff to transfer between centers
An estimated `r abs(final[["Northeast Regional Office"]]$staff.move)` FIS Is/IIs need to be moved `r ifelse(final[["Northeast Regional Office"]]$staff.move > 0, print("to"), print("from"))` Northeast Regional Office to balance caseloads across all centers:

```{r Northeast Regional Office staffing, echo=FALSE, message=FALSE, warning=FALSE}
summary %>% filter(Center == "Northeast Regional Office")  %>% select(-`Center Code`, -Center) %>% kable()
```



# Hilton Heights
### Cases to transfer between centers
When cases are realigned, most of the cases coming to Hilton Heights will be coming from `r final[["Hilton Heights"]]$transfer1` and `r final[["Hilton Heights"]]$transfer2`.

```{r Hilton Heights transfers, echo=FALSE, message=FALSE, warning=FALSE}
print(planning[["Hilton Heights"]]$transfers.graph)
```

### Current spread of redeterminations
When cases are realigned, the month of `r final[["Hilton Heights"]]$month.highest` will have the most redeterminations while the month of `r final[["Hilton Heights"]]$month.lowest` will have the fewest.

```{r Hilton Heights redets, echo=FALSE, message=FALSE, warning=FALSE}
print(planning[["Hilton Heights"]]$redets.graph)
```

In order to ensure that redeterminations are done evenly throughout the year, there should be about `r final[["Hilton Heights"]]$month.avg` cases processed each month. To achieve that, cases should be moved as such:
`r kable(planning[["Hilton Heights"]]$redets)`

### Staff to transfer between centers
An estimated `r abs(final[["Hilton Heights"]]$staff.move)` FIS Is/IIs need to be moved `r ifelse(final[["Hilton Heights"]]$staff.move > 0, print("to"), print("from"))` Hilton Heights to balance caseloads across all centers:

```{r Hilton Heights staffing, echo=FALSE, message=FALSE, warning=FALSE}
summary %>% filter(Center == "Hilton Heights")  %>% select(-`Center Code`, -Center) %>% kable()
```